---
title: "p8015_hw1_tl2882"
author: "Tian Li"
date: 2018-09-14
output:
  github_document
---

```{r include = FALSE}
library(tidyverse)
```

# Problem 1

## Create a data frame
```{r}
set.seed(1)

df = tibble(
  random_sample = runif(10, min = 0, max = 5),
  vec_logical = (random_sample > 2),
  vec_char = c("A", "B", "C", "D", "E", "a", "b", "c", "d", "e"),
  vec_factor = factor(c("A", "B", "C", "D", "E", "a", "b", "c", "d", "e"))
)
```

## Try to take the mean
```{r}
mean(df$random_sample)
mean(df$vec_logical)
mean(df$vec_char)
mean(df$vec_factor)
```

1.Succeed: normal arithmetical mean  
2.Succeed: "ture" means "1", and "false" means "0"  
3.Fail: only numeric or logical vector can calculate the mean  
4.Fail: only numeric or logical vector can calculate the mean

## Convert variables

### Applies the as.numeric function
```{r eval = FALSE}
as.numeric(df$vec_logical)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)
```

What happens? two warnings.

1. Succeed ("ture" is converted to "1", and "false" is converted to "0")  
2. Fail: can't be converted to numeric  
3. Succeed : can be converted to numbers which represent their alphabetical order

